Interpolate weight at agecl output to annual age

### 2020-06-05 InterpolateWeightAtAge.Rmd
now works for oldest ages

---
title: "Interpolate the weight at agecl output to annual age"
author: "Sarah Gaichas"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    code_fold: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(here)
library(tidyverse)
library(atlantisom)
library(ggthemes)

@@

# plot portion, just redfish, capelin is blank and cod looks the same
library(ggforce)
survObsFullWtAtAge[[1]][[2]] + facet_wrap_paginate(~species, ncol=1, nrow = 1, page=3, scales = "free")

@@

annages <- annageRed
wtagecl <- wtageRed
fgs <- fgs

@@

  # complex, but works for 2 ages/agecl, need to test more, need to fix oldest
  # for more than 2 ages/agecl need to have a bigger lead/lag
  # achieved by faking a scalar for lead/lag n using max() function
  # should be ceiling I think for odd NumAgeClassSize, but not sure?
  wtage_out <- wtage_out %>%
    dplyr::select(species, time, trueage, NumAgeClassSize, agecl, avgage) %>%
    dplyr::left_join(wtagecl_inc) %>%
    dplyr::group_by(species, time) %>%
    dplyr::mutate(wtIntage = case_when(
      (agecl==1 & trueage<avgage) ~ (1-(avgage-trueage)/avgageinc)*increment,
      (agecl>1 & trueage<avgage) ~
        (1-(avgage-trueage)/avgageinc)*increment +
        lag(atoutput, ceiling(max(NumAgeClassSize)/2)),
      (trueage>avgage) ~
        ((trueage-avgage)/lead(avgageinc, ceiling(max(NumAgeClassSize)/2)))*lead(increment, ceiling(max(NumAgeClassSize)/2)) + atoutput
    ))

@@

Try the updated function again, any bugs with multiple species? OK so far.

@@

Last issue is extrapolating the oldest wt at age. Linear from the last one?

>>>>

---
title: "Interpolate weight at agecl output to annual age"
author: "Sarah Gaichas"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    code_fold: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(here)
library(tidyverse)
library(atlantisom)
library(ggthemes)
library(ggforce)

@@

# plot portion, just redfish, capelin is blank and cod looks the same
#library(ggforce)
survObsFullWtAtAge[[1]][[2]] + facet_wrap_paginate(~species, ncol=1, nrow = 1, page=3, scales = "free")

@@

annages <- annageRed
wtagecl <- wtageRed
fgs <- NOBAom_redcodcap$funct.group_ss

@@

  # complex, but works for 2 ages/agecl, need to test more, need to fix oldest
  # for more than 2 ages/agecl need to have a bigger lead/lag
  # achieved by faking a scalar for lead/lag n using max() function
  # should be ceiling I think for odd NumAgeClassSize, but not sure?
  # for oldest age(s), perhaps default=last(x) in lead statement
  wtage_out <- wtage_out %>%
    dplyr::select(species, time, trueage, NumAgeClassSize, agecl, avgage) %>%
    dplyr::left_join(wtagecl_inc) %>%
    dplyr::group_by(species, time) %>%
    dplyr::mutate(wtIntage = case_when(
      (agecl==1 & trueage<avgage) ~ (1-(avgage-trueage)/avgageinc)*increment,
      (agecl>1 & trueage<avgage) ~
        (1-(avgage-trueage)/avgageinc)*increment +
        dplyr::lag(atoutput, ceiling(max(NumAgeClassSize)/2)),
      (trueage>avgage) ~
        (trueage-avgage)/dplyr::lead(avgageinc, ceiling(max(NumAgeClassSize)/2), default=last(avgageinc))*dplyr::lead(increment, ceiling(max(NumAgeClassSize)/2), default=last(increment)) + atoutput
    ))

@@

Try the updated function again, any bugs with multiple species? Is it getting the weight at max age for both? OK so far.

@@

Extrapolating the oldest wt at age is now linear from the last agecl weight at age using default=last() in the dplyr::lead() calls.
